---
title: "Swirl"
author: "Esau_Moreno"
date: "16 November 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Install swirl. Since swirl is an R package, you can easily install it by entering a single command from the R console:

```{r}
install.packages("swirl")
```

### If you've installed swirl in the past make sure you have version 2.2.21 or later. You can check this with:

```{r}
packageVersion("swirl")
```

### Load swirl. Every time you want to use swirl, you need to first load the package. From the R console:

```{r}
library(swirl)
```

### Install the R Progroamming course. Swirl offers a variety of interactive courses, but for our purposes, you want the one called R Programming. Type the following from the R prompt to install this course:

```{r}
install_from_swirl("R Programming")
```

### Start swirl and complete the lessons. Type the following from the R console to start swirl:
```{r}
swirl()
```
---
Then, follow the menus and select the R Programming course when given the option. For the first part of this course you should complete the following lessons:

1.Basic Building Blocks
2.Workspace and Files
3.Sequences of Numbers
4.Vectors
5.Missing Values
6.Subsetting Vectors
7.Matrices and Data Frames

If you need help...

Visit the Frequently Asked Questions (FAQ) page to see if you can answer your own question immediately.


Good luck and have fun!

For more information on swirl, visit swirlstats.com
---